Human Endogenous Retroviral Transcripts Show Potential as Novel, Tumor Specific Biomarkers for Colorectal Cancer

### 2021-01-19 manuscript/main.tex
add pandoc citation conversion and fix docx formatting

problems with AMA style file
https://tex.stackexchange.com/questions/55020/updated-ama-bst-file
i modified vancouver.bst to get proper author lists

>>>>

%% citation issues
- problems with AMA style file
- https://tex.stackexchange.com/questions/55020/updated-ama-bst-file
- i modified vancouver.bst to get proper author lists > myvancouver.bst
- pandoc conversion to docx requires csl
- wget -O ama.csl https://github.com/citation-style-language/styles/blob/master/american-medical-association.csl?raw=true

%% word format issues
- see https://pandoc.org/MANUAL.html, --reference-doc= for DOCX
- To produce a custom reference.docx, first get a copy of the default reference.docx:
pandoc --print-default-data-file reference.docx > custom-reference.docx
Then open custom-reference.docx in Word, modify the styles as you wish, and save the file.
Modified: Normal, Abstract, Author, Title, Subtitle, Heading 1, Heading 2, Bibliography, Body Text, First Paragraph, Verbatim Char
